Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys

### 2023-02-02 paper/elsarticle/main.tex
minor updates

	One of the promising control techniques came with the formation of model predictive control~\cite{Morari_MPC}. MPC provides optimal control input based on minimization of a specified cost function, while considering model of the system. Compared to linear quadratic controllers (LQR)~\cite{LQR}, model predictive control also includes constraints on the control input or process variables~\cite{Maciejowski_MPC}, so further saturation is not necessary. Moreover, as the optimization problem is solved in every control step, MPC represents a receding horizon control~\cite{receding_horizon} which has a significant benefit mainly in the terms of disturbance rejection.

@@

	In this approach, the aggressivity is adjusted based on the ratio between the reference step change and the maximal reference step change that can be realized during the control operation:
	\begin{eqnarray}
		\label{eq:rho_delta_ref}
		\rho(k) = \frac{\vert \Delta_{\mathrm{ref}}(k) \vert}{\Delta_{\max}},
	\end{eqnarray} 
	where $\Delta_{\mathrm{ref}}(k) = y_{\mathrm{ref}}(k) - y_{\mathrm{ref}}(k-1)$ is the size of the reference step change. The denominator of Eq.~\eqref{eq:rho_delta_ref} is changed as well. In contrast to the maximal deviation from the steady state in Section~\ref{sec:self_tunable}, this approach introduces $\Delta_{\max}$ as the maximal possible reference step change given by: $\Delta_{\max} = \Vert \Delta_{\mathrm{ref}}(k) \Vert_{\infty}, \forall k \ge 0 $. 
	Analogously to the original approach, the maximal reference step can be set based on the general knowledge of the expected future reference values. Another option is to exploit the information about the system constraints and set the parameter $\Delta_{\max}$ according to Eq.~\eqref{eq:d_max}.

>>>>

	One of the promising control techniques came with the formation of model predictive control~\cite{Morari_MPC}. MPC provides optimal control input based on minimization of a specified cost function, while considering model of the system. Compared to linear quadratic controllers (LQR)~\cite{LQR}, model predictive control also includes constraints on the control input or process variables~\cite{Maciejowski_MPC}, so further saturation is not necessary. Moreover, as the optimization problem is solved in every control step, MPC represents a receding horizon control~\cite{receding_horizon} which has a significant benefit mainly in the terms of disturbance rejection. The model predictive control was intensively investigated in connection with heat exchangers. In~\cite{Vinaya_HE_MPC}, the authors developed a model predictive control for a shell and tube heat exchanger. In~\cite{Oravec_energy}, the robust MPC of a plate heat exchanger with soft constraints was analyzed. Four robust control strategies were presented and compared in~\cite{Oravec_HE_ATE}. A two-level control structure was applied on a heat exchanger network in ~\cite{Gonzales_HE_MPC}. In this study, the low level of control was ensured by MPC and the high level by a supervisory online optimiser.

@@

	In this approach, the aggressivity is adjusted based on the ratio between the reference step change and the maximal reference step change that can be realized during the control operation:
	\begin{eqnarray}
		\label{eq:rho_delta_ref}
		\rho(k) = \frac{\vert \Delta_{\mathrm{ref}}(k) \vert}{\Delta_{\max}},
	\end{eqnarray} 
	where $\Delta_{\mathrm{ref}}(k) = y_{\mathrm{ref}}(k) - y_{\mathrm{ref}}(k-1)$ is the size of the reference step change. The denominator of Eq.~\eqref{eq:rho_delta_ref} is changed as well. In contrast to the maximal deviation from the steady state in Section~\ref{sec:self_tunable}, this approach introduces $\Delta_{\max}$ as the maximal possible reference step change. Analogously to the original approach, the maximal reference step can be set based on the general knowledge of the expected future reference values, i.e., $\Delta_{\max} = \Vert \Delta_{\mathrm{ref}}(k) \Vert_{\infty}, \forall k \ge 0 $. 
	Another option is to exploit the information about the system constraints and set the parameter $\Delta_{\max}$ according to Eq.~\eqref{eq:d_max}.
